\textbf{Computational Fuzzy Extractors}

### 2013-05-17 CompFuzzExt.tex
clean up

\begin{abstract} 
%\lnote{This is an old abstract, no longer correct}
Fuzzy extractors derive cryptographically strong keys from noisy sources.  They are traditionally built by combining a secure sketch and a randomness extractor.  Secure sketches remove noise from the source while revealing little information about the source.  Randomness extractors convert high entropy sources to the uniform distribution.  %Secure sketches necessarily reveal some information about the noisy secret, and thus the derived key in fuzzy extractors has lower entropy than the source.  The minimal entropy loss 
%One-message information reconciliation protocols called secure sketches remove noise
%from secrets without revealing too much about them.  They are a crucial ingredient in
%fuzzy extractors, which provide an information-theoretic mechanism for reliable key derivation from noisy sources.

Secure sketches necessarily reveal some information about the noisy secret.
% and thus the key derived by fuzzy extractors has lower entropy than the source.  
The minimal entropy loss is dictated by bounds on error-correcting codes.  
Fuzzy extractors constructed using secure sketches suffer a similar entropy loss.  This entropy loss decreases the length of the derived key.  
%suffer from similar bounds imposed by coding theory.

We ask whether these bounds can be overcome by considering computational, rather than information-theoretic, secure sketches and fuzzy extractors.  %The answer we provide an answer for both secure sketches and fuzzy extractors.  
The answer to this question is mixed, For secure sketches the answer is no, and for fuzzy extractors the answer is yes.
\begin{itemize}
\item \textbf{Secure Sketches:} We show that a secure sketch that retains a large amount of HILL pseudo entropy implies a secure sketch which retains a similar amount of information-theoretic entropy.  We also consider a weaker computational notion of security, the unpredictability of a source conditioned on output of the secure sketch.  We show that in order to correct $t$ errors, the unpredictability of a source must decrease with the volume of a ball of radius $t$.
\item \textbf{Fuzzy Extractors:}  We show these impossibility results can be overcome by analyzing fuzzy extractors directly.  Namely, we show how to build a \emph{lossless} computational fuzzy extractor for uniform sources and certain other sources of high entropy~(namely, symbol-fixing sources, where each dimension is either uniform or fixed), based on the hardness of the Learning with Errors~(LWE) problem.  This construction requires us to show that the decision version of LWE is secure when a small number of dimension has no error---a result that may be of independent interest.
\end{itemize}
%mixed, and building them based on the Learning with Errors (LWE) problem.  We thus obtain the first secure sketch with no loss in entropy.   More specifically, our contributions are as follows:
%
%\begin{itemize}
%\item \textbf{New Definitions:} In seeking the right computational relaxation of the information-theoretic definition of a secure sketch, we rule out most natural one, which uses HILL pseudoentropy.  We do so by demonstrating that a secure sketch defined via HILL pseudoentropy is subject to the same coding-based  bounds as the information-theoretic secure sketch.  We then find a different relaxation, using unpredictability entropy, and show that it can be used to construct computational fuzzy extractors.
%
%
%\item \textbf{New Construction:} We build a lossless secure sketch for uniform sources and certain other sources of high entropy (namely, symbol-fixing sources, in which each dimension is either uniform or fixed),  based on the hardness of the LWE problem.  This construction requires us to show that the decision version of LWE is secure when a small number of dimensions have no error---a result that may be of independent interest.
%\end{itemize}
\end{abstract}

@@

\section{\consref{cons:informal construction} with Nonuniform Sources}
\subsection{\consref{cons:informal construction} with Symbol Fixing Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational fuzzy extractor for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

@@

%\bnote{We need to be clear about notation here.  Why are $x, e$ sometimes bold and sometimes capital?} 
\begin{proof}
We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.  If the blocks are fixed to some other value the reduction is essentially the same.

@@

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
%\bnote{This should be if $\vb' | A$ is uniformly distributed, then $\vb |A $ is uniformly distributed.}
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.

>>>>

\begin{abstract} 
Fuzzy extractors derive strong keys from noisy sources.  Their
security is defined information-theoretically, which limits the length
of the derived key, sometimes making it too short to be useful. We ask
whether it is possible to obtain longer keys by considering
computational security, and show the following.

\begin{itemize}
\item\textbf{Negative Result:} Noise tolerance in fuzzy extractors is usually
achieved using an information reconciliation component called a ``secure
sketch.'' The security of this component, which directly affects the
length of the resulting key, is subject to lower bounds from coding
theory.  We show that, even when defined computationally, secure
sketches are still subject to lower bounds from coding theory. Specifically, we consider
two computational relaxations of the information-theoretic security requirement of secure sketches, using conditional HILL entropy and unpredictability entropy. For both cases we show  that computational secure sketches cannot outperform the best information-theoretic secure sketches in the case of high-entropy Hamming metric sources.

\item\textbf{Positive Result:} We show that the negative result can be overcome by
analyzing computational fuzzy extractors directly.  Namely, we show
how to build a computational fuzzy extractor whose output key length
equals the entropy of the source (this is impossible in the
information-theoretic setting). Our construction is based on the
hardness of the Learning with Errors (LWE) problem, and is secure when
the noisy source is uniform or symbol-fixing (that is, each dimension
is either uniform or fixed). As part of the security proof, we show a result of independent interest, namely
that the decision version of LWE is secure even when a small number of
dimensions has no error.
\end{itemize}
\end{abstract}

@@

\section{Computational Fuzzy Exactor with Nonuniform Sources}
\label{sec:LWE block fixing sources}
In this section, we show the security of~\consref{cons:informal construction} is preserved for certain high entropy distributions.  Showing security of a computational fuzzy extractor for arbitrary high min-entropy distributions is an open problem.  First we recall the notion of a symbol fixing source~(from~\cite{KZ07}): 
\begin{definition}
Let $W = (W_1,..., W_{m+\alpha})$ be a distribution where $W_i$ takes values over $\{0,1\}^b$, we say that a distribution is a $m$-\emph{symbol fixing source} if $H_\infty(W)\geq mb$ and for all $W_i$ one of the following conditions is met:
\begin{itemize}
\item $W_i \overset{d}= U_b$
\item There exists a value $c_i$ such that $\Pr[W_i = c_i] =1$.
\end{itemize}
\end{definition}
%A block fixing source is an extension of a entropy source where each bit is independently random or fixed to larger alphabets.

@@

\begin{proof}
We assume that all of the fixed blocks are located at the end and their fixed value is $0$, that is, $W_{m+1}, ..., W_{m+\alpha} =0$.  If the blocks are fixed to some other value the reduction is essentially the same.

@@

It suffices to show that $\D'$ properly prepares a random instance for the distinguisher.  We show this in three claims: 
\begin{enumerate}
\item If $\vA'$ is a random matrix then $\vA$ is a random matrix.
\item If $\vb'$ is uniformly distributed conditioned on $\vA'$ then $\vb$ is uniformly distributed conditioned on $\vA$.
\item If $\vb' = \vA'\vx'+\ve'$ then $\exists \vx$~(uniformly distributed) such that $\vb = \vA \vx + \ve'$ where the last $\alpha$ coordinates of $\ve'$ are $0$ and $\ve_i' = \ve_i$ for $1\leq i\leq m$.
\end{enumerate}
\begin{figure}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.
